%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% \usepackage[sfdefault]{FiraSans}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    % \scshape removed to prevent font error
    \textbf{\Huge Bryan Lee Wen Swen} \\ \vspace{1pt}
    \small (+60) 10 650 6632 $|$ 
    \href{mailto:bryanlee13579@gmail.com}{\underline{bryanlee13579@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/bryan-lee-wen-swen/}{\underline{linkedin.com/in/bryan-lee-wen-swen}} $|$
    \href{https://github.com/Sodiumchloridy}{\underline{github.com/Sodiumchloridy}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universiti Tunku Abdul Rahman}{Sungai Long, Selangor}
      {Bachelor of Science, Software Engineering (Honours) $|$ CGPA: 3.85/4.0}{Expected Jun 2026}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern (PaySuite Department)}{Jun 2025 -- Present}
      {Worldline International}{Kuala Lumpur, Malaysia}
      \resumeItemListStart
        \resumeItem{Architected and pioneered a Playwright automation test suite, reducing reliance on manual regression testing and enabling continuous integration checks for a credit card processing platform.}
        \resumeItem{Developed a Retrieval-Augmented Generation (RAG) chatbot using LLMs to automate internal FAQ retrieval; experimented with embedding models to optimize performance for resource-constrained environments.}
        \resumeItem{Engineered a document conversion pipeline to automatically turn user manuals documents into a modern documentation website.}
        \resumeItem{Maintained and optimized a full-stack payments platform (Angular/Spring Boot); resolved complex production bugs including pagination logic failures, indeterminate checkbox states, and backend user deletion constraints.}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Research Assistant (Part-time)}{Sep 2024 -- Jun 2025}
      {Universiti Tunku Abdul Rahman}{Sungai Long, Selangor}
      \resumeItemListStart
        \resumeItem{Co-authored ``Enhancing Deepfake Detection Generalization: A Scalable and Real-Time Detection'', a paper published in Springer's Lecture Notes in Networks and Systems (LNNS) (Scopus Indexed).}
        \resumeItem{Fine-tuned a YOLOv11 computer vision model on Tesla P100 GPUs, achieving 96.7\% validation accuracy in detecting AI-generated faces across mixed datasets.}
        \resumeItem{Engineered an end-to-end data pipeline for dataset curation (FFHQ), augmentation, and real-time inference benchmarking using Generative Adversarial Networks (PGGAN).}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance Full Stack Developer}{Oct 2024 -- Sep 2025}
      {Treehole Story}{Remote}
      \resumeItemListStart
        \resumeItem{Led a major framework upgrade from Next.js 14 to 15, refactoring 8,400+ lines of code to resolve breaking changes, update UI components and improve functionality.}
        \resumeItem{Designed and implemented a nested/threaded comments system on the Laravel backend by introducing parent-child comment relationships and restructuring API endpoints.}
        \resumeItem{Resolved production bugs including broken pagination controls and login modal triggers; added responsive mobile layouts, emoji keyboard support, and page animations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Manga-Website} $|$ \emph{Next.js, MongoDB, Tailwind CSS, External APIs}}{}
          \resumeItemListStart
            \resumeItem{Built a responsive full-stack manga discovery and reading platform with server-side rendering.}
            \resumeItem{Integrated external REST APIs for content retrieval and implemented server-side caching to reduce redundant API calls and improve page load performance.}
            \resumeItem{Implemented internationalization (i18n) to support multiple languages for a global user base.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------HONORS & AWARDS-----------
% Corrected list structure
\section{Honors \& Awards}
\resumeItemListStart
    \resumeItem{First Prize in Competition for Artificial Intelligence Generated Content (AIGC) 2023 in Fu Zhou, China}
    \resumeItem{1st Runner-up, Ethereum Kuala Lumpur 2023 Hackathon: Aleo Bounty Track}
    \resumeItem{Top 20\% Globally (Stage 1), WorldQuant International Quant Championship 2024}
\resumeItemListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item\small{
        \textbf{Languages}{: Java, JavaScript/TypeScript, Python, C++, PHP (Laravel), HTML/CSS, SQL} \\
        \textbf{Frameworks}{: Spring Boot, Angular, React, Next.js, PyTorch, Tailwind CSS} \\
        \textbf{Tools \& Platforms}{: Docker, Apache Kafka, Git/GitLab, PostgreSQL, Cypress, DBeaver, Ollama, LiteLLM} \\
        \textbf{Spoken Languages}{: English, Chinese, Malay, Hokkien/Cantonese (Conversational)}
    }
 \end{itemize}


%-------------------------------------------
\end{document}